Sorting algorithms: how are they affected by memory faults?

### 2019-12-21 paper/DataAnalysis.tex
continuação da escrita.

Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following tables illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
    \cline{2-4} 
     & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
    \hline
    copy & adsad & asdasd & asdasd \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-ueq}
    \end{center}
\end{table}

@@

@@

We produced graphs with the same data about dependent variables showed in tables before. Figure X shows an example of these graphs.

>>>>

Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of unordered elements quantity (\%UEQ)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 3.07 & 3.0 & 1.64 & 0.0 & 6.0 \\
    \hline
    0.01 & 100 & insertion & 10.87 & 11.0 & 1.59 & 8.0 & 14.0 \\
    \hline
    0.05 & 10000 & merge & 28.32 & 28.34 & 0.31 & 27.69 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 19.56 & 19.58 & 0.26 & 18.95 & 20.07 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-ueq}
    \end{center}
\end{table}

@@

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of largest subarray size (\%LSS)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 67.4 & 71.0 & 15.84 & 38.0 & 100.0 \\
    \hline
    0.01 & 100 & insertion & 19.77 & 20.0 & 3.11 & 14.0 & 27.0 \\
    \hline
    0.05 & 10000 & merge & 0.19 & 0.2 & 0.03 & 0.15 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 0.3 & 0.3 & 0.03 & 0.23 & 0.34 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-lss}
    \end{center}
\end{table}

@@

We produced graphs with the same data showed in Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss}. Figure \ref{fig-distribution-all-algorithms-001-all-sizes} shows an example of these graphs. On it, we illustrate on the top-left graph that, considering the mean, bubblesort produces fewer unordered elements related to the total than other algorithms.

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.20]{figures/Estatisticas_por_Algoritmo_Prob_001.png}}
    \caption{Distribution data with \textit{probability of failure} of 0.01, all algorithms and \textit{array sizes}.}
    \label{fig-distribution-all-algorithms-001-all-sizes}
\end{figure}

\subsection{Dependente Variables Normality}

An essential step to continue the analysis is to verify if dependent variables have a normal distribution. In this work, we produced the Q-Q plot to analyze the normality visually. We also ran the Shapiro-Wilk \cite{shapiro1965analysis} test to confirm if they follow a normal distribution or not.

After the Shapiro-Wilk test, we determine that only the dependent variable \%UEQ (\textit{percentage of unordered elements quantity}) has a normal distribution related to mean for all algorithms. This situation occurs considering all possible combinations between independent variables: \textit{sorting algorithm}, \textit{probability of failure} and \textit{array size}.

Based on these results, we choose to test just the hypothesis associated with the dependent variable \%UEQ. We make use of the ANOVA method to test the hypothesis, and this method is premised the normal distribution of variables values.

Tables \ref{table-shapiro-test-lss} and \ref{table-shapiro-test-ueq} shows examples of results we get running Shapiro-Wilk test. The independent variables assume these values: \textit{probability of failure} of 0.01 and \textit{array size} of 100. The bold \textit{p-values} confirms that the data is normally distributed.

\begin{table}[H]
    \parbox{.45\linewidth}{
        \caption{Shapiro-Wilk test for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.}
        \begin{center}
        \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
        \hline
        Bubblesort & 0.854840 & 0.0007 \\
        \hline
        Insertion Sort & 0.961790 & \textbf{0.3439} \\
        \hline
        Mergesort & 0.937173 & \textbf{0.0763} \\
        \hline
        Quicksort & 0.869708 & 0.0016 \\
        \hline
        \end{tabular}
        \label{table-shapiro-test-lss}
        \end{center}
    }
    \hfill
    \parbox{.45\linewidth}{
        \caption{Shapiro-Wilk test for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.}
        \begin{center}
        \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
        \hline
        Bubblesort & 0.934980 & \textbf{0.0666} \\
        \hline
        Insertion Sort & 0.949881 & \textbf{0.1678} \\
        \hline
        Mergesort & 0.936667 & \textbf{0.0739} \\
        \hline
        Quicksort & 0.936049 & \textbf{0.0712} \\
        \hline
        \end{tabular}
        \label{table-shapiro-test-ueq}
        \end{center}
    }
\end{table}

Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution. Figure \ref{fig-qqplot-lss-001-100} below presents this graph for the dependent variable \textit{percentage of the largest subarray size} considering a \textit{probability of failure} of 1\% and a \textit{array size} of 100 for all sorting algorithms.

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Largest_subarray_size.png}}
    \textsf{\caption[Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.]{Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.\label{fig-qqplot-lss-001-100}}}
 \end{figure}

 Figure \ref{fig-qqplot-ueq-001-100} shows the same graph for the dependent variable \textit{percentage of unordered elements quantity} considering same values for independent variables.

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Perc_unordered_elements_quantity.png}}
    \textsf{\caption[Q-Q plot for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.]{Q-Q plot for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.\label{fig-qqplot-ueq-001-100}}}
\end{figure}

### 2019-12-21 paper/article.tex
continuação da escrita.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

>>>>

% \subsection{Figures and Tables}
% \paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
% bottom of columns. Avoid placing them in the middle of columns. Large 
% figures and tables may span across both columns. Figure captions should be 
% below the figures; table heads should appear above the tables. Insert 
% figures and tables after they are cited in the text. Use the abbreviation 
% ``Fig.~\ref{fig}'', even at the beginning of a sentence.

% \begin{table}[htbp]
% \caption{Table Type Styles}
% \begin{center}
% \begin{tabular}{|c|c|c|c|}
% \hline
% \textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
% \cline{2-4} 
% \textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
% \hline
% copy& More table copy$^{\mathrm{a}}$& &  \\
% \hline
% \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
% \end{tabular}
% \label{tab1}
% \end{center}
% \end{table}

% Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
% rather than symbols or abbreviations when writing Figure axis labels to 
% avoid confusing the reader. As an example, write the quantity 
% ``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
% units in the label, present them within parentheses. Do not label axes only 
% with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
% \{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
% quantities and units. For example, write ``Temperature (K)'', not 
% ``Temperature/K''.

% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
% acknowledgments in the unnumbered footnote on the first page.
